---
name: Francisco
surname: d'Albertas Gomes de Carvalho
position: "Research Associate"
address: "Conservation Research Institute (UCCRI),
Department of Zoology,University of Cambridge"
#phone: +55 11 99121 8851
email: "fd370@cam.ac.uk"
www: fdalbertas.com
#twitter: FdAlbertas
github: franciscodalbertas
linkedin: franciscodalbertas
headcolor: "414141"
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    keep_tex: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me

I am a landscape ecologist with master’s and doctoral training in ecology. My work focuses on nature-based solutions that promote biodiversity conservation and climate change mitigation. I assess the ecological and economic impacts of conservation strategies, such as ecological restoration, with a particular emphasis on carbon credit projects as a tool to deliver credible and effective outcomes. Throughout my career, I have oriented my work toward applied questions, with the goal of informing policy and guiding real-world conservation decisions. Currently, I work at the University of Cambridge, leading research on the carbon and biodiversity outcomes of tropical restoration.

# Skills & Languages

## **Technical**: R, GIS, Google Earth Engine, Data Analysis, Spatial Prioritization, Ecosystem Service Modelling 

## **Conservation Practice**: Ecological Restoration, Policy Analysis, Writing & Communication 

## **Languages**: Portuguese (native), English (fluent), French (advanced), Spanish (intermediate)


# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD in Ecology - 'Paths for an ecological intensification of agriculture through restoration and agriculture certification' ", "2017-2022", "Universidade de São Paulo with 1 year as visiting researcher at the University of Cambridge", "São Paulo, Brasil",
  "Master in Ecology - 'Edge effects modulation of carbon stocks in fragmented Atlantic Forest landscapes'", "2013-2015", "Universidade de São Paulo", "São Paulo, Brasil",
  "Biological Sciences degree", "2006-2011", "Universidade de São Paulo", "São Paulo, Brasil",
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Professional experience

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Research associate","2024 - Present","Conservation Research Institute,Department of Zoology,University of Cambridge","Cambridge, UK",
  "Researcher and data scientist at the project Trade, Development and the Environment HUB","2022-2024","International Institute for Sustainability-IIS","Rio de Janeiro, Brazil",
  "Researcher - Sao Paulo Research Foundation Training fellowship  as part of the Biodiversity and Ecosystem Service Scenarios Network (ScenNet)", "2015-2017", "Laboratório de Ecologia da Paisagem e Conservação-LEPaC(Departmento de Ecologia, Universidade de São Paulo) ", "São Paulo, Brasil",
  "Junior environmental analyst (Internship) - Protected Areas Monitoring Programe", "2012-2013", "Instituto Socioambiental - ISA", "São Paulo, Brasil",
  "Junior environmental analyst (Internship) - Oil and mining environmental impact evaluation ", "2011-2012", "Mineral Engenharia e Ambiente", "São Paulo, Brasil",
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Selected Consultancies

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Evaluating the baseline condition of priority ecosystem services at watersheds potentially threatened by mining operation in Minas Gerais State","2021","Aquaflora providing services to Vale S.A.","São Paulo, Brazil", 
  "Monitoring deforestation and fire within Amazonia and Cerrado protected areas", "2020-2021", "World Wildlife Fund - WWF Brazil ", "São Paulo, Brasil",
  "Mapping threats to federal and state protected areas in Brazil", "2017-2018", "Instituto Socioambiental - ISA ", "São Paulo, Brasil",
  "Designing ecological corridors between indigenous lands", "2016", "Klabin s/a Papel e Celulose ", "Paraná, Brasil",
  " Floristic inventory of urban areas in Sao Paulo", "2016", "Bloomberg Philanthropies e Global Road Safety ", "São Paulo, Brasil"
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Teaching

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Professor - Co-organized and taught short course Landscape Use for master’s students in management.","2022", "Fundação Getulio Vargas", "Rio de Janeiro, Brazil" 
  
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# List of Publications

- Borges-Matos, C., **d’Albertas, F.**, Mendes, M.E., Loyola, R., Metzger, J.P., 2025. Combining protection and restoration strategies enables cost-effective compensation with ecological equivalence in Brazil. Environmental Impact Assessment Review 114, 107922. https://doi.org/10.1016/j.eiar.2025.107922

- Balmford, A., Ball, T.S., Balmford, B., Bateman, I.J., Buchanan, G., Cerullo, G., **d’Albertas, F.**, Eyres, A., Filewod, B., Fisher, B., Green, J.M.H., Hemes, K.S., Holland, J., Lam, M.S., Naidoo, R., Pfaff, A., Ricketts, T.H., Sanderson, F., Searchinger, T.D., Strassburg, B.B.N., Swinfield, T., Williams, D.R., 2025. Time to fix the biodiversity leak. Science 387, 720–722. https://doi.org/10.1126/science.adv8264

- Cerullo, G., Worthington, T., Brancalion, P., Brandão, J., **d’Albertas, F.**, Eyres, A., Swinfield, T., Edwards, D., Balmford, A., 2024. Conflicts and opportunities for commercial tree plantation expansion and biodiversity restoration across Brazil. Global Change Biology 30, e17208. https://doi.org/10.1111/gcb.17208

- Cesar de Oliveira, S.E.M., Nakagawa, L., Lopes, G.R., Visentin, J.C., Couto, M., Silva, D.E., **d’Albertas, F.**, Pavani, B.F., Loyola, R., West, C., 2024. The European Union and United Kingdom’s deforestation-free supply chains regulations: Implications for Brazil. Ecological Economics 217, 108053. https://doi.org/10.1016/j.ecolecon.2023.108053

- **d’Albertas, F.**, Rocha, D., Lacerda, E., Niemeyer, J., Oliveira, L.G., Capellão, R., Pavani, B.F., Monteiro de Almeida Rocha, J., 2024. Spatial model of land value for the Brazilian territory with 1km resolution. https://doi.org/10.5281/zenodo.10476110

- **d’Albertas, F.**, Sparovek, G., Pinto, L.-F.G., Hohlenwerger, C., Metzger, J.-P., 2023. Yield increases mediated by pollination and carbon payments can offset restoration costs in coffee landscapes. One Earth. https://doi.org/10.1016/j.oneear.2023.11.007

- González-Chaves, A.D., Carvalheiro, L.G., Piffer, P.R., **d’Albertas, F.**, Giannini, T.C., Viana, B.F., Metzger, J.P., 2023. Evidence of time-lag in the provision of ecosystem services by tropical regenerating forests to coffee yields. Environ. Res. Lett. 18, 025002. https://doi.org/10.1088/1748-9326/acb161

- Berger, I., Dicks, L.V., **d’Albertas, F.**, 2023. Quantify wild areas that optimize agricultural yields. Nature 622, 697–697. https://doi.org/10.1038/d41586-023-03312-y

- **d’Albertas, F.**, Ruggiero, P., Pinto, L.F.G., Sparovek, G., Metzger, J.P., 2023. Agricultural certification as a complementary tool for environmental law compliance. Biological Conservation 277, 109847. https://doi.org/10.1016/j.biocon.2022.109847

- Pashkevich, M.D., **d’Albertas, F.**, Aryawan, A.A.K., Buchori, D., Caliman, J.-P., Chaves, A.D.G., Hidayat, P., Kreft, H., Naim, M., Razafimahatratra, A., Turner, E.C., Zemp, D.C., Luke, S.H., 2022. Nine actions to successfully restore tropical agroecosystems. Trends in Ecology & Evolution. https://doi.org/10.1016/j.tree.2022.07.007

- **d’Albertas, F.**, González-Chaves, A., Borges-Matos, C., Zago de Almeida Paciello, V., Maron, M., Metzger, J.P., 2021. Private reserves suffer from the same location biases of public protected areas. Biological Conservation 261, 109283. https://doi.org/10.1016/j.biocon.2021.109283

- Acosta, A.L., **d’Albertas, F.**, Leite, M. de S., Saraiva, A.M., Metzger, J.P.W., 2018. Gaps and limitations in the use of restoration scenarios: a review. Restoration Ecology 26, 1108–1119. https://doi.org/10.1111/rec.12882

- **d’Albertas, F.**, Costa, K., Romitelli, I., Barbosa, J.M., Vieira, S.A., Metzger, J.P., 2018. Lack of evidence of edge age and additive edge effects on carbon stocks in a tropical forest. Forest Ecology and Management 407, 57–65. https://doi.org/10.1016/j.foreco.2017.09.042

- Metzger, J.P., Esler, K., Krug, C., Arias, M., Tambosi, L., Crouzeilles, R., Acosta, A.L., Brancalion, P.H., **d’Albertas, F.**, Duarte, G.T., Garcia, L.C., Grytnes, J.-A., Hagen, D., Jardim, A.V.F., Kamiyama, C., Latawiec, A.E., Rodrigues, R.R., Ruggiero, P.G., Sparovek, G., Strassburg, B., Saraiva, A.M., Joly, C., 2017. Best practice for the use of scenarios for restoration planning. Current Opinion in Environmental Sustainability 29, 14–25. https://doi.org/10.1016/j.cosust.2017.10.004





```{r}
#library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")
#x <- bibliography_entries("my_pubs.bib")
# bibliography_entries("my_pubs.bib") %>%
#   arrange(desc(issued))



```


