---
name: Francisco
surname: d'Albertas
position: "mestre em ecologia"
address: "Departmento de Ecologia, Instituto de Biosciências, Universidade de São Paulo"
phone: +55 11 99121 8851
#www: 
email: "francisco.albertas@gmail.com"
twitter: FdAlbertas
#github: mariecurie
#linkedin: mariecurie
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
#bibliography: references.bib  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me

My name is Francisco d’Albertas Gomes de Carvalho. I am a biologist with a Master and an ongoing Ph.D. in Ecology – to be concluded in January 2021 – with 10 years’ experience working with applied research focusing on understanding how the spatial pattern of human-modified landscapes affects biodiversity, ecosystem services provision and the Climate. 


# Skills

## R - markdown - SIG - Arcmap & QGIS -data gattering and analysis - modelling ecoystem services - restoration planning - writing and commmunication -  MapBiomas -  Google Earth Engine 

# Languages

## Portuguese (native) - English (fluent) - French (advanced) - Spanish (intermediate)


# Formação

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "P.h.D in Ecology", "2017-2021", "Universidade de São Paulo", "São Paulo, Brazil",
  "Master in Ecology", "2013-2015", "Universidade de São Paulo", "São Paulo, Brazil",
  "Bachelor in Biological Sciences", "2006-2011", "Universidade de São Paulo", "São Paulo, Brazil",
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Experiência profissional

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Consult - Análise periódica de desmatamento e fogo em Áreas Protegidas na Amazônia e no Cerrado", "2020-2021", "World Wildlife Fund - WWF Brazil ", "São Paulo, Brasil",
  "Consultor - Mapeamento sistemático de pressões e ameaças à Áreas Protegidas Federais e Estaduais", "2017-2018", "Instituto Socioambiental - ISA ", "São Paulo, Brasil",
  "Consultor - Planejamento de corredores ecológicos entre Terras Indígenas como parte de um EIA", "2016", "Klabin s/a Papel e Celulose ", "Paraná, Brasil",
  "Consultor - Inventário florístico para planejamento urbano", "2016", "Bloomberg Philanthropies e Global Road Safety ", "São Paulo, Brasil",
  "Analista ambiental junior (estágio) - Programa de monitoramento de áreas protegidas", "2012-2013", "Instituto Socioambiental - ISA", "São Paulo, Brasil",
  "Analista ambiental junior (estágio)p - Análise de impacto ambientalde projetos de óleo e mineração ", "2011-2012", "Mineral Engenharia e Ambiente", "São Paulo, Brasil",
  "Gestor ambiental (estágio) - gestão de parques urbanos", "2009-2010", "Secretaria de Meio Ambiente do Estado de São Paulo", "São Paulo, Brasil",
  "Gestor ambiental (estágio) - gestão de parques urbanos e educação ambiental", "2008-2009", "Secretaria Municipal de Meio Ambiente de São Paulo", "São Paulo, Brasil",
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

\newpage

# Experiência em Pesquisa

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  
  "Pesquisador visitante - Colaboração com o grupo de pesquisa de Andrew Balmford (Conservation Science Group), para desenvolver parte do meu doutorado;", "2020-2021", "University of Cambridge ", "Cambridge, Reino Unido",
  "Técnico de pesquisa - Bolsa técnica da FAPESP para fazer parte da organização Biodiversity and Ecosystem Service Scenarios Network (ScenNet)", "2015-2017", "Laboratório de Ecologia da Paisagem e Conservação-LEPaC(Departmento de Ecologia, Universidade de São Paulo) ", "São Paulo, Brasil",
  
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publicações

**d’Albertas, F.**, González-Chaves, A., Borges-Matos, C., Zago de Almeida Paciello, V., Maron, M., Metzger, J.P., 2021. Private reserves suffer from the same location biases of public protected areas. Biological Conservation 261, 109283. https://doi.org/10.1016/j.biocon.2021.109283

Helena Fany Pantaleoni RIcardo; Alicia Rolla; Silvia Futada; **Francisco d'Albertas G. de Carvalho**. 2019. O estado das áreas protegifas: Garimpo ilegal nas UCs e TIs da Amazônia Brasileira. https://bit.ly/3sIxequ

Acosta, A.L., **d’Albertas, F.**, Leite, M. de S., Saraiva, A.M., Metzger, J.P.W., 2018. Gaps and limitations in the use of restoration scenarios: a review. Restoration Ecology 26, 1108–1119. https://doi.org/10.1111/rec.12882

**d’Albertas, F.**, Costa, K., Romitelli, I., Barbosa, J.M., Vieira, S.A., Metzger, J.P., 2018. Lack of evidence of edge age and additive edge effects on carbon stocks in a tropical forest. Forest Ecology and Management 407, 57–65. https://doi.org/10.1016/j.foreco.2017.09.042

Metzger, J.P., Esler, K., Krug, C., Arias, M., Tambosi, L., Crouzeilles, R., Acosta, A.L., Brancalion, P.H., **d’Albertas, F.**, Duarte, G.T., Garcia, L.C., Grytnes, J.-A., Hagen, D., Jardim, A.V.F., Kamiyama, C., Latawiec, A.E., Rodrigues, R.R., Ruggiero, P.G., Sparovek, G., Strassburg, B., Saraiva, A.M., Joly, C., 2017. Best practice for the use of scenarios for restoration planning. Current Opinion in Environmental Sustainability, Part A: Environmental change issues • Part B: Open Issue, Part III 29, 14–25. https://doi.org/10.1016/j.cosust.2017.10.004

```{r}
#library(dplyr)

#knitr::write_bib(c("vitae", "tibble"), "packages.bib")

# bibliography_entries("references.bib") %>%
#   arrange(desc(author$family), issued)
```

